Generating reliable services' composition using A-policies: a model-driven approach\thanks{This work is partially financed by the projects {\sc Orchestra} ECOS-ANUIES, {\sc Clever} STIC-AMSUD, and {\sc Masai}.}

### 2013-10-31 CAISE2011/submitted/caise-etal.tex
CAISE2011 y algo mas

%% This is file `elsarticle-template-1a-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1a-num.tex 151 2009-10-08 05:18:25Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1a-num.tex $
%%
\documentclass[preprint,12pt]{elsarticle}
\usepackage{geometry}
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

\journal{Journal of Systems and Software}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{$\pi$SOD-M: A Methodology for Building Service-Oriented Applications in
the Presence of Non-Functional Properties}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[inst1]{Pl\'acido A. Souza Neto}
\author[inst2]{Genoveva Vargas-Solar}
\author[inst3]{Martin A. Musicante}
\author[inst4]{Valeria~de~Castro}
\author[inst3]{Umberto Costa}

\address[inst1]{Federal Institute of Rio Grande do Norte -- Natal-RN,
Brazil}

\address[inst2]{Universit\'e de Grenoble -- Saint Martin d'H\`{e}res, France}

\address[inst3]{Federal University of Rio Grande do Norte -- Natal-RN,
Brazil}

\address[inst4]{Universidad Rey Juan Carlos -- M\'{o}stoles, Spain}

\begin{abstract}
This paper presents\ldots
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text

Service oriented computing is at the origin of an evolution in the field of software development. 
An important challenge of service oriented development is  to ensure the alignment between IT systems and the business logic.
%dealing thereby with the promise that IT systems can  evolve  according to the business needs. 
Thus, organizations are  seeking for mechanisms to deal with the gap between the systems developed and business needs \cite{bell}. The literature stresses the need for methodologies and techniques for service oriented analysis and design, claiming that they are the cornerstone  in the development of meaningful services' based applications \cite{5}.  In this context, some authors argue that the convergence of model-driven software development, service orientation and better techniques for documenting and improving business processes are the key to make real the idea of rapid, accurate development of software that serves, rather than dictates, software users' goals \cite{watson}.

@@

%..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--
%\noindent{\bf\em 
\subsection{Programming non-functional properties for services}
%..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--
Current standards in services' composition implement functional, non-functional constraints and communication aspects by combining different languages and protocols. WSDL and SOAP among others are languages used respectively for describing services' interfaces and message exchange protocols for calling methods exported by such services. For adding a transactional behaviour to a services' composition it is necessary to implement WS-Coordination, WS-Transaction, WS-BussinessActivity and WS-AtomicTransaction. The selection of the adequate protocols for adding a specific non-functional constraints to a services' composition (e.g., security, transactional behaviour and adaptability) is responsibility of a programmer. As a consequence, the development of an application based on a services' composition is a complex and a time-consuming process. This is opposed to the philosophy of services that aims at facilitating the integration of distributed applications. Other works, like \cite{helga2}
introduce a model for transactional services composition based on
an advanced transactional model. \cite{samy} proposes an approach
that consists of a set of algorithms and rules to assist designers
to compose transactional services. In \cite{Vid04} the model
introduced in \cite{schuldt-etal-TODS} is extended to web services
for addressing atomicity.

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{plain}
\bibliography{biblio}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1a-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

@@

%%
%% End of file `elsarticle-template-1a-num.tex'.

>>>>

\documentclass{llncs}
\usepackage{geometry}
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\begin{document}

\title{Generating reliable services' composition  using A-policies: a model-driven approach\thanks{This work is partially financed by the projects {\sc Orchestra} ECOS-ANUIES, {\sc Clever} STIC-AMSUD, and {\sc Masai}.}}

\author{Genoveva Vargas-Solar\inst{1}
\and Valeria de Castro\inst{4}
\and Pl\'{a}cido Antonio de Souza Neto\thanks{Financed by CAPES/STIC-AMSUD Brasil, BEX 4112/11-3} \inst{5,6}
\and Javier A. Espinosa-Oviedo\inst{3}
\and Esperanza Marcos\inst{4}
\and Martin A. Musicante\inst{5}
\and Jos\'{e}-Luis Zechinelli-Martini\inst{2,1}
\and Christine Collet \inst{3}}

\institute{
	French Council of Scientific Research, LIG-LAFMIA	\\
	681 Rue de la Passerelle, BP. 72, 38402	Saint Martin d'H\`{e}res Cedex, France		\\
		\email{Genoveva.Vargas-Solar@imag.fr}
\and
	Fundaci\'{o}n Universidad de las Am\'{e}ricas, Puebla	\\
	Exhacienda Sta. Catarina M\'{a}rtir s/n 72820, San Andr\'{e}s Cholula, Puebla, M\'{e}xico			\\
	\email{joseluis.zechinelli@udlap.mx}
\and
	Grenoble Institute of Technology	\\
	46 Avenue F'{e}lix Viallet, 38031 Grenoble Cedex 1		\\
	\email{Christine.Collet@grenoble-inp.fr}, \email{Javier.Espinosa@imag.fr} \\
\and
	Universidad Rey Juan Carlos	\\
	Av Tulip\'{a}n, M\'{o}stoles, Spain 		\\
	\email{Valeria.deCastro@urjc.es, esperanza.marcos@urjc.es} \\
\and
	DIMAp - UFRN, ForAll - Formal Methods and Language Research Laboratory	\\
	Campus Universitário - Lagoa Nova, Natal - RN, Brasil		\\
	\email{mam@dimap.ufrn.br} \\
	\and
	Instituto Federal do Rio Grande do Norte	\\
	Av. Senador Salgador Filho, 1559 - Tirol, Natal - RN, Brasil		\\
	\email{placido.neto@ifrn.edu.br}
}

\maketitle

\begin{abstract}
This paper presents an approach for modeling and associating {\em A-Policies} to  services' based applications. It proposes to extend the SOD-M model driven method with   (i) the $\pi$-{\sc SCM} an {\em A-Policy} services' composition meta-model for representing non-functional constraints associated to services' based applications;  (ii) the $\pi$-{\sc Pews} meta-model providing guidelines for expressing the composition and the policies; and, (iii)  model to model and model to text transformation rules for semi-automatizing the implementation of reliable services' compositions.
As will be shown within our environment implementing these meta models and rules, one may represent both systems' cross-cutting aspects (e.g., exception handling for describing what to do when a service is not available, recovery, persistence aspects) and constraints associated to services, that must be respected for using them (e.g., the fact that a service requires an authentication protocol for executing a method). 
\end{abstract}

%*********************************************************************************************************
\section{Introduction}
%*********************************************************************************************************
Service oriented computing is at the origin of an evolution in the field of software development. 
An important challenge of service oriented development is  to ensure the alignment between IT systems and the business logic.
%dealing thereby with the promise that IT systems can  evolve  according to the business needs. 
Thus, organizations are  seeking for mechanisms to deal with the gap between the systems developed and business needs \cite{bell}. The literature stresses the need for methodologies and techniques for service oriented analysis and design, claiming that they are the cornerstone  in the development of meaningful services' based applications \cite{5}.  In this context, some authors argue that the convergence of model-driven software development, service orientation and better techniques for documenting and improving business processes are the key to make real the idea of rapid, accurate development of software that serves, rather than dictates, software users' goals \cite{watson}.

@@

%..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--
%\noindent{\bf\em 
\subsection{Programming non-functional properties for services}
%..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--..--
Current standards in services' composition implement functional, non-functional constraints and communication aspects by combining different languages and protocols. WSDL and SOAP among others are languages used respectively for describing services' interfaces and message exchange protocols for calling methods exported by such services. For adding a transactional behaviour to a services' composition it is necessary to implement WS-Coordination, WS-Transaction, WS-BussinessActivity and WS-AtomicTransaction. The selection of the adequate protocols for adding a specific non-functional constraints to a services' composition (e.g., security, transactional behaviour and adaptability) is responsibility of a programmer. As a consequence, the development of an application based on a services' composition is a complex and a time-consuming process. This is opposed to the philosophy of services that aims at facilitating the integration of distributed applications. Other works, like \cite{helga2}
introduce a model for transactional services composition based on
an advanced transactional model. \cite{samy} proposes an approach
that consists of a set of algorithms and rules to assist designers
to compose transactional services. In {\cite{Vid04} the model
introduced in \cite{schuldt-etal-TODS} is extended to web services
for addressing atomicity.

@@

\bibliographystyle{plain}
\bibliography{caise,S-Coord,Bib/e-commerce,Bib/trans,Bib/Component,Bib/XML,Bib/Workflow,Bib/SODM,Bib/G,Bib/docbi}

%*********************************************************************************************************
%\section*{Appendix}\label{sec:appendix}
%*********************************************************************************************************
%Figure \ref{fig:mappingrules-1} shows the transformation rules between the $\pi$-SCM meta-model to the $\pi$-{\sc Pews}  meta-model.
%\begin{figure}
%\includegraphics[width=1.0\textwidth]{figs/Mapping-1}
%\caption{Mapping rules between $\pi$-SCM  and $\pi$-{\sc Pews} meta-models}
%\label{fig:mappingrules-1}
%\end{figure}

%\begin{figure}
%\includegraphics[width=0.70\textwidth]{figs/Mapping-3}
%\caption{Mapping rules between $\pi$-SCM meta-model and $\pi$-{\sc Pews} policy elements}
%\label{fig:mappingrules-3}
%\end{figure}

%\begin{figure}
%\includegraphics[width=0.70\textwidth]{figs/Mapping-2}
%\caption{Mapping rules between $\pi$-SCM meta-model and $\pi$-{\sc Pews} rule elements}
%\label{fig:mappingrules-2}
%\end{figure}

@@
